---
title: "rmarkdown template"
date: "February 25, 2021"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 3
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---
^ this is the YAML header. 
This is where you specify what output doc type you want (HTML, PDF, Word), and what kind of Table Of Contents you'd like.

# Formatting:

# Header 1
## Header 2
### Header 3

etc. 

Use an asterisk to provide emphasis, such as *italics* or **bold**.
Bullets are made with a star:

* Item 1
* Item 2
* Item 3

You can use latex math mode in an r markdown document!
$\int_2^3 x^2 \, dx=\frac{3^3}{3}-\frac{2^3}{3}=\frac{19}{3}$
(Hover over this to see what it produces)

More info here:
<http://rmarkdown.rstudio.com>.
<https://bookdown.org/yihui/rmarkdown/html-document.html#appearance-and-style>
Cheat sheet: 
<https://rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf>
Math mode (useful for writing equations): 
<https://www1.cmc.edu/pages/faculty/aaksoy/latex/latexthree.html#>

# Code chunks:

Embed code like so:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Use three apostrophes and *DESCRIPTIVE* names in curly brackets! (makes debugging easier).
Within the curly brackets, can include **eval = TRUE/FALSE** (runs code in code chunk, default is TRUE), **echo = TRUE/FALSE** (displays code in output doc, default is TRUE). 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r desc}
library(tidyverse)
library(kableExtra)
library(ggplot2)

# This is a descriptive table where we can input variables
rbind(
  id = "Patient ID", 
  stime = "Survival time in days",
  death = "Death status (0 = alive; 1 = dead)",
  treatment = "Treatment received (Neutrons, Photons)",
  site = "Site of cancer (Bladder, Cervix, Prostate, Rectum)",
  phase = "Randomisation phase (0 = first phase; 1 = second phase)",
  meta = "Metastases diagnosed before death (Yes, No)",
  metatime = "Time to metastases (days)",
  death1year = "Death within 1 year of recruitment (Yes, No)"
)  %>%
  kbl(col.names = "Description") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = T,
                font_size = 15) %>%
                scroll_box(height = "300px")

path=dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(path)
```
